|

### 2018-12-14 paper.Rmd
Corrected typos and added orca() function.

* **Access**: Research is normally funded by taxpayers (researchers are also taxpayers). Hence, it should be freely accessible to everyone without any barriers, e.g., without requiring commercial software. Importantly, researchers from developing countries are even more dependent on free access to knowledge [@Kirsop2005-ro].
* **Reproducability**: Even if you have written a study and analyzed the data yourself you will forget what you did after a few months. A fully reproducible setup will help you to trace back your own steps. Obviously, the same is true for other researchers who may want to understand your work and built on it. It may sound like a joke but why not aim for a document that can be used to reproduce your findings in in 500 years. 
* **Errors**: Manual steps in data analysis (e.g., manually copy/pasting values into a table etc.) may introduce errors. R Markdown allows you to **automatize** such steps and/or avoid them.
* **Revisions**: Revising a paper takes much less time if you have all the code you need in one place, i.e., one `.rmd` file. For instance, if you decide to exclude a subset of your data you simply need to insert one line of your code at the beginning and everything is rebuilt/re-estimated automatically.

@@

## Plotly graphs
Plotly is a popular graph engine that let's you also produce interactive graphs that you can embed in html webpages or documents (e.g., see [here](https://paulcbauer.shinyapps.io/visualizing-causal-scenarios/)). I am a big fan. For some time there was no easy, automatic way to insert high resolution Plotly graphs into your R Markdown PDF. However, this changed since Plotly provided Orca, a command line application for generating static images from Plotly graphs. The installation is a bit tricky (see here: https://github.com/plotly/orca#installation) but once you get it running you can produce beautiful graphs and include them in your RMarkdown PDF using some simple latex as shown below in Figure \@ref(fig:fig-3).

@@

* Keep all files of your project (that matter for producing the PDF) in one folder without subfolders. You can zip and directly upload that folder to the [Harvard dataverse](https://dataverse.harvard.edu/)).
* Make sure that filenames have a logic to them.
    + Main file with text/code: "paper.rmd", "report.rmd" 
    + Data files: "data_xxxxxx.*"
    + Image files: "fig_xxxxxx.*"
    + Tables files: "table_xxxx.*"
    + etc.
    + Ideally, your filenames will correspond to the names in the paper. For instance, Figure 1 in the paper may have a corresponding file called `fig_1_xxxxx.pdf`.
* Use document the document outline in R studio (Ctrl + Shift + O) when you work with R Markdown.
* Name rchunks according to what they do or produce:
    + "`fig-...`" for chunks producing figures
    + "`table-...`" for chunks producing tables
    + "`model-...`" for chunks producing model estimates
    + "`import-...`" for chunks importing data
    + "`recoding-...`" for chunks in which data is recoded
* Use "really" informative variable names:
    + Q: What do you think does the variable *trstep* measure? It actually measures trust in the European parliament. 
        + How could we call this variable instead? Yes, `trust.european.parliament` which is longer but will probably be understood by one of your descendants in 100 years.
    + If your setup is truly reproducible you will probably re-use the variable names that you generate as variable names in the tables you produce. Hence, there is an incentive to use good names.
* Use unique identifiers in the final document:
    + e.g., name the models you estimate "M1", "M2" etc.
    + These unique names should also appear in the published paper.
    + Think of someone who wants to produce Figure 1/Model 1 in your paper but doesn't find it in your code...

>>>>

* **Access**: Research is normally funded by taxpayers (researchers are also taxpayers). Hence, it should be freely accessible to everyone without any barriers, e.g., without requiring commercial software. Importantly, researchers from developing countries are even more dependent on free access to knowledge [@Kirsop2005-ro].
* **Reproducability**: Even if you have written a study and analyzed the data yourself you will forget what you did after a few months. A fully reproducible setup will help you to trace back your own steps. Obviously, the same is true for other researchers who may want to understand your work and built on it. It may sound like a joke but why not aim for a document that can be used to reproduce your findings in 500 years. 
* **Errors**: Manual steps in data analysis (e.g., manually copy/pasting values into a table etc.) may introduce errors. R Markdown allows you to **automatize** such steps and/or avoid them.
* **Revisions**: Revising a paper takes much less time if you have all the code you need in one place, i.e., one `.rmd` file. For instance, if you decide to exclude a subset of your data you simply need to insert one line of your code at the beginning and everything is rebuilt/re-estimated automatically.

@@

## Plotly graphs
Plotly is a popular graph engine that let's you also produce interactive graphs that you can embed in html webpages or documents (e.g., see [here](https://paulcbauer.shinyapps.io/visualizing-causal-scenarios/)). I am a big fan. For some time there was no easy, automatic way to insert high resolution Plotly graphs into your R Markdown PDF. However, this changed since Plotly provided Orca, a command line application for generating static images from Plotly graphs. The installation is a bit tricky (see here: https://github.com/plotly/orca#installation) but once you get it running you can produce beautiful graphs and include them in your RMarkdown PDF using some simple latex as shown below in Figure \@ref(fig:fig-3). Potentially, in case you did not install the command line application this part may fail. If so simply exclude the chunk and the latex code.

@@

* Keep all files of your project (that matter for producing the PDF) in one folder without subfolders. You can zip and directly upload that folder to the [Harvard dataverse](https://dataverse.harvard.edu/).
* Make sure that filenames have a logic to them.
    + Main file with text/code: "paper.rmd", "report.rmd" 
    + Data files: "data_xxxxxx.*"
    + Image files: "fig_xxxxxx.*"
    + Tables files: "table_xxxx.*"
    + etc.
    + Ideally, your filenames will correspond to the names in the paper. For instance, Figure 1 in the paper may have a corresponding file called `fig_1_xxxxx.pdf`.
* Use the document outline in R studio (Ctrl + Shift + O) when you work with R Markdown.
* Name rchunks according to what they do or produce:
    + "`fig-...`" for chunks producing figures
    + "`table-...`" for chunks producing tables
    + "`model-...`" for chunks producing model estimates
    + "`import-...`" for chunks importing data
    + "`recoding-...`" for chunks in which data is recoded
* Use "really" informative variable names:
    + Q: What do you think does the variable *trstep* measure? It actually measures trust in the European parliament. 
        + How could we call this variable instead? Yes, `trust.european.parliament` which is longer but will probably be understood by another researcher. 
    + If your setup is truly reproducible you will probably re-use the variable names that you generate as variable names in the tables you produce. Hence, there is an incentive to use good names.
* Use unique identifiers in the final document:
    + e.g., name the models you estimate "M1", "M2" etc.
    + These unique names should also appear in the published paper.
    + Think of someone who wants to produce Figure 1/Model 1 in your paper but doesn't find it in your code...

### 2018-12-14 paper.tex
Corrected typos and added orca() function.

  \title{\vspace{1cm}Writing a reproducible paper\\
in R Markdown*\footnote{*Corresponding address:
  \href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}.
  Acknowledgments: I am grateful to all those generous people that
  invest their time into open-source software.}\vspace{0.5cm}\\}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
    \author{Paul C. Bauer\\
Mannheim Centre for European Social Research}
    \preauthor{\centering\large\emph}
  \postauthor{\par}
      \predate{\centering\large\emph}
  \postdate{\par}
    \date{13 December, 2018\\[2\baselineskip]Feedback?\\
\href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}\\}

@@

\begin{itemize}
\tightlist
\item
  \textbf{Access}: Research is normally funded by taxpayers (researchers
  are also taxpayers). Hence, it should be freely accessible to everyone
  without any barriers, e.g., without requiring commercial software.
  Importantly, researchers from developing countries are even more
  dependent on free access to knowledge (Kirsop and Chan
  \protect\hyperlink{ref-Kirsop2005-ro}{2005}).
\item
  \textbf{Reproducability}: Even if you have written a study and
  analyzed the data yourself you will forget what you did after a few
  months. A fully reproducible setup will help you to trace back your
  own steps. Obviously, the same is true for other researchers who may
  want to understand your work and built on it. It may sound like a joke
  but why not aim for a document that can be used to reproduce your
  findings in in 500 years.
\item
  \textbf{Errors}: Manual steps in data analysis (e.g., manually
  copy/pasting values into a table etc.) may introduce errors. R
  Markdown allows you to \textbf{automatize} such steps and/or avoid
  them.
\item
  \textbf{Revisions}: Revising a paper takes much less time if you have
  all the code you need in one place, i.e., one \texttt{.rmd} file. For
  instance, if you decide to exclude a subset of your data you simply
  need to insert one line of your code at the beginning and everything
  is rebuilt/re-estimated automatically.
\end{itemize}

@@

Plotly is a popular graph engine that let's you also produce interactive
graphs that you can embed in html webpages or documents (e.g., see
\href{https://paulcbauer.shinyapps.io/visualizing-causal-scenarios/}{here}).
I am a big fan. For some time there was no easy, automatic way to insert
high resolution Plotly graphs into your R Markdown PDF. However, this
changed since Plotly provided Orca, a command line application for
generating static images from Plotly graphs. The installation is a bit
tricky (see here: \url{https://github.com/plotly/orca\#installation})
but once you get it running you can produce beautiful graphs and include
them in your RMarkdown PDF using some simple latex as shown below in
Figure \ref{fig:fig-3}.

@@

\begin{itemize}
\tightlist
\item
  Keep all files of your project (that matter for producing the PDF) in
  one folder without subfolders. You can zip and directly upload that
  folder to the \href{https://dataverse.harvard.edu/}{Harvard
  dataverse}).
\item
  Make sure that filenames have a logic to them.

  \begin{itemize}
  \tightlist
  \item
    Main file with text/code: ``paper.rmd'', ``report.rmd''
  \item
    Data files: ``data\_xxxxxx.*"
  \item
    Image files: ``fig\_xxxxxx.*"
  \item
    Tables files: ``table\_xxxx.*"
  \item
    etc.
  \item
    Ideally, your filenames will correspond to the names in the paper.
    For instance, Figure 1 in the paper may have a corresponding file
    called \texttt{fig\_1\_xxxxx.pdf}.
  \end{itemize}
\item
  Use document the document outline in R studio (Ctrl + Shift + O) when
  you work with R Markdown.
\item
  Name rchunks according to what they do or produce:

@@

    \begin{itemize}
    \tightlist
    \item
      How could we call this variable instead? Yes,
      \texttt{trust.european.parliament} which is longer but will
      probably be understood by one of your descendants in 100 years.
    \end{itemize}
  \item
    If your setup is truly reproducible you will probably re-use the
    variable names that you generate as variable names in the tables you
    produce. Hence, there is an incentive to use good names.
  \end{itemize}
\item
  Use unique identifiers in the final document:

>>>>

  \title{\vspace{1cm}Writing a reproducible paper\\
in R Markdown*\footnote{*Corresponding address:
  \href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}.
  Acknowledgments: I am grateful to all those generous people that
  invest their time into open-source software.}\vspace{0.5cm}\\}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
    \author{Paul C. Bauer\\
Mannheim Centre for European Social Research}
    \preauthor{\centering\large\emph}
  \postauthor{\par}
      \predate{\centering\large\emph}
  \postdate{\par}
    \date{14 December, 2018\\[2\baselineskip]Feedback?\\
\href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}\\}

@@

\begin{itemize}
\tightlist
\item
  \textbf{Access}: Research is normally funded by taxpayers (researchers
  are also taxpayers). Hence, it should be freely accessible to everyone
  without any barriers, e.g., without requiring commercial software.
  Importantly, researchers from developing countries are even more
  dependent on free access to knowledge (Kirsop and Chan
  \protect\hyperlink{ref-Kirsop2005-ro}{2005}).
\item
  \textbf{Reproducability}: Even if you have written a study and
  analyzed the data yourself you will forget what you did after a few
  months. A fully reproducible setup will help you to trace back your
  own steps. Obviously, the same is true for other researchers who may
  want to understand your work and built on it. It may sound like a joke
  but why not aim for a document that can be used to reproduce your
  findings in 500 years.
\item
  \textbf{Errors}: Manual steps in data analysis (e.g., manually
  copy/pasting values into a table etc.) may introduce errors. R
  Markdown allows you to \textbf{automatize} such steps and/or avoid
  them.
\item
  \textbf{Revisions}: Revising a paper takes much less time if you have
  all the code you need in one place, i.e., one \texttt{.rmd} file. For
  instance, if you decide to exclude a subset of your data you simply
  need to insert one line of your code at the beginning and everything
  is rebuilt/re-estimated automatically.
\end{itemize}

@@

Plotly is a popular graph engine that let's you also produce interactive
graphs that you can embed in html webpages or documents (e.g., see
\href{https://paulcbauer.shinyapps.io/visualizing-causal-scenarios/}{here}).
I am a big fan. For some time there was no easy, automatic way to insert
high resolution Plotly graphs into your R Markdown PDF. However, this
changed since Plotly provided Orca, a command line application for
generating static images from Plotly graphs. The installation is a bit
tricky (see here: \url{https://github.com/plotly/orca\#installation})
but once you get it running you can produce beautiful graphs and include
them in your RMarkdown PDF using some simple latex as shown below in
Figure \ref{fig:fig-3}. Potentially, in case you did not install the
command line application this part may fail. If so simply exclude the
chunk and the latex code.

@@

\begin{itemize}
\tightlist
\item
  Keep all files of your project (that matter for producing the PDF) in
  one folder without subfolders. You can zip and directly upload that
  folder to the \href{https://dataverse.harvard.edu/}{Harvard
  dataverse}.
\item
  Make sure that filenames have a logic to them.

  \begin{itemize}
  \tightlist
  \item
    Main file with text/code: ``paper.rmd'', ``report.rmd''
  \item
    Data files: ``data\_xxxxxx.*"
  \item
    Image files: ``fig\_xxxxxx.*"
  \item
    Tables files: ``table\_xxxx.*"
  \item
    etc.
  \item
    Ideally, your filenames will correspond to the names in the paper.
    For instance, Figure 1 in the paper may have a corresponding file
    called \texttt{fig\_1\_xxxxx.pdf}.
  \end{itemize}
\item
  Use the document outline in R studio (Ctrl + Shift + O) when you work
  with R Markdown.
\item
  Name rchunks according to what they do or produce:

@@

    \begin{itemize}
    \tightlist
    \item
      How could we call this variable instead? Yes,
      \texttt{trust.european.parliament} which is longer but will
      probably be understood by another researcher.
    \end{itemize}
  \item
    If your setup is truly reproducible you will probably re-use the
    variable names that you generate as variable names in the tables you
    produce. Hence, there is an incentive to use good names.
  \end{itemize}
\item
  Use unique identifiers in the final document:
